Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
merged back in some missing stuff

@@

\subsection{Context Factors}
Context factors for projects were assessed by Zhang et et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

>>>>

\subsection{Discussion}
Most of the studies we examined used open-source datasets which is in line with previous recommendations (\cite{Catal}, \cite{Vandecruys}). The two papers which used Windows Vista were not proposing a new or improved fault prediction model but were instead analyzing Microsoft's organizational structure to see how it may have affected bug levels. Although the NASA software isn't open source, we think that its datasets are acceptable because of their domain and the fact that NASA has made the datasets public for research purposes. Research has heeded the recommendations of earlier researchers and now primarily use open-source datasets

@@

\subsection{Context Factors}
Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
